### 2020-05-31 writeup/transfer.tex
sec 3 wip

Based on the key lemma, we provide rigorous explanations to the phenomena of negative transfer in multi-task learning.
We study three components, including task model, data size and covariate shift.
For each component, we show how negative transfer occurs using a simplified isotropic model.
Then, we describe the algorithmic consequence of the theory.

@@

It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
As a warmup, we first describe an example that rigorously formalizes the connection using our setup.

>>>>

Based on Lemma \ref{lem_cov_shift_informal}, we rigorously explain the phenomena of negative transfer in multi-task learning.
We explain from three perspectives, including \textit{task model}, \textit{data size} and \textit{covariate shift}.
We show how negative transfer occurs as a result in a simplified model and describe the algorithmic consequence.

@@

It is well-known since the seminal work of Caruana \cite{C97} that how well multi-task learning performs depends on task relatedness.
We formalize this connection in the following simplified setting.
